---
title: "Main paper Results"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r gph_parameters_and_packages, include=FALSE}

library("ggplot2")
library("knitr")
library("ggeffects")

theme <-   theme(text = element_text(size = 10),
                 panel.background = element_rect(fill = "white"),
                 plot.margin = unit(c(0.1,0.1,0.1,0), "cm"),
                 axis.line = element_line(size = 0.5),
                 axis.line.x = element_line(color="black"),
                 axis.line.y = element_line(color="black"),
                 legend.key = element_blank(),
                 legend.key.size = unit(0.3,"cm"),
                 legend.position = "bottom",
                 legend.background = element_rect(colour = "black"),
                 strip.background = element_rect(fill = "grey95"))

```

```{r load_data, include=FALSE}


load("./crstatistics_phase_1.RData")
dta1.stat <- dta.stat



load("./crstatistics_phase_2.RData")
dta2.stat <- dta.stat
rm(dta.stat)

dta2.stat$relsetrunc <- ifelse(dta2.stat$relse>30, 30,dta2.stat$relse)



```


## Phase 1

### Summarise scenarios

```{r scenarios1}
print("Number of scenarios:")

 length(unique(dta1.stat$scenario))
 
print("ICC:")

 kable(table(dta1.stat$ICC))

print("Correlation structure:")

 kable(table(dta1.stat$Correlation_structure))
 
print("Sequences:")

 kable(table(dta1.stat$Sequences))
 
print("Clusters:")

 kable(table(dta1.stat$clusters))

print("Cluster size:")

 kable(table(dta1.stat$Mean_cluster_size))

 kable(table(dta1.stat$Varying_cluster_size))
 

```

### Convergence



```{r convergence}
summary(dta1.stat$convergep)
```


### Bias

```{r bias_histograms}
ggplot(data = subset(dta1.stat, mdl %in% c("fg.cmp")), aes(x = stdbias)) + 
  facet_wrap( ~ wc) +
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey80", size = 1)+
  geom_vline(xintercept = -10, linetype = "longdash", color = "grey80", size = 1)+
  geom_vline(xintercept = 10, linetype = "longdash", color = "grey80", size = 1) +
  geom_histogram(bins = 15) + 
  xlab("Intervention effect estimate standardised bias") +
  scale_y_continuous(breaks = 2 * 0:6) +
  theme

ggsave("./output/phase1_rxbias.pdf", width = 16, height = 12, units = "cm")
```


```{r bias_numbers}
round(summary(dta1.stat$stdbias), 3)

round(summary(dta1.stat$pbias), 3)
```


### Standard errors
```{r se_histograms}

ggplot(data = subset(dta1.stat, dfname == "cmp"), aes(x = relse)) + 
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey80", size = 0.5) +
  geom_vline(xintercept = -10, linetype = "longdash", color = "grey80", size = 0.5) +
  geom_vline(xintercept = 10, linetype = "longdash", color = "grey80", size = 0.5) +
  geom_histogram(bins = 35) + 
  facet_grid(SA ~ wc) +
  scale_y_continuous(breaks = function(x) c(0,floor(x[2]))) +
  xlab("Standard error relative error (%)") +
  theme

ggsave("./output/phase1_se.emf", width = 16, height = 12, units = "cm")
ggsave("./output/phase1_se.eps", width = 16, height = 12, units = "cm")



ggplot(data = subset(dta1.stat, dfname == "cmp"), aes(x = relse, fill = Correlation_structure)) + 
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey80", size = 0.5) +
  geom_vline(xintercept = -10, linetype = "longdash", color = "grey80", size = 0.5) +
  geom_vline(xintercept = 10, linetype = "longdash", color = "grey80", size = 0.5) +
  geom_histogram(bins = 35) + 
  facet_grid(SA ~ wc) +
  scale_y_continuous(breaks = function(x) c(0,floor(x[2]))) +
  xlab("Standard error relative error (%)") +
  theme

ggsave("./output/phase1_se_Corr_str.pdf", width = 16, height = 12, units = "cm")

ggplot(data = subset(dta1.stat, dfname == "cmp"), aes(x = relse, fill = ICC)) + 
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey80", size = 0.5) +
  geom_vline(xintercept = -10, linetype = "longdash", color = "grey80", size = 0.5) +
  geom_vline(xintercept = 10, linetype = "longdash", color = "grey80", size = 0.5) +
  geom_histogram(bins = 35) + 
  facet_grid(SA ~ wc) +
  scale_y_continuous(breaks = function(x) c(0,floor(x[2]))) +
  xlab("Standard error relative error (%)") +
  theme

ggsave("./output/phase1_se_ICC.pdf", width = 16, height = 12, units = "cm")


ggplot(data = subset(dta1.stat, dfname == "cmp"), aes(x = relse, fill = Varying_cluster_size)) + 
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey80", size = 0.5) +
  geom_vline(xintercept = -10, linetype = "longdash", color = "grey80", size = 0.5) +
  geom_vline(xintercept = 10, linetype = "longdash", color = "grey80", size = 0.5) +
  geom_histogram(bins = 35) + 
  facet_grid(SA ~ wc) +
  scale_y_continuous(breaks = function(x) c(0,floor(x[2]))) +
  xlab("Standard error relative error (%)") +
  theme

ggsave("./output/phase1_se_Varying_cluster_size.pdf", width = 16, height = 12, units = "cm")


ggplot(data = subset(dta1.stat, dfname == "cmp"), aes(x = relse, fill = Sequences)) + 
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey80", size = 0.5) +
  geom_vline(xintercept = -10, linetype = "longdash", color = "grey80", size = 0.5) +
  geom_vline(xintercept = 10, linetype = "longdash", color = "grey80", size = 0.5) +
  geom_histogram(bins = 35) + 
  facet_grid(SA ~ wc) +
  scale_y_continuous(breaks = function(x) c(0,floor(x[2]))) +
  xlab("Standard error relative error (%)") +
  theme

ggsave("./output/phase1_se_Sequences.pdf", width = 16, height = 12, units = "cm")
```


```{r se_numbers}

setNames(aggregate(relse ~ sa , 
                   data = subset(dta1.stat, dfname=="cmp"), 
                   FUN = function(x) round(summary(x), 3)), rep("",2))


aggregate(relse ~ sa , 
          data = subset(dta1.stat, dfname=="cmp"), 
          FUN = function(x) round(c(n = sum(!is.na(x)),
                                    n10 = sum(abs(x) > 10) ,
                                    p10 = 100 * sum(abs(x) > 10) / sum(!is.na(x)), 
                                    n8 = sum(abs(x) > 8) ,
                                    p8 = 100 * sum(abs(x) > 8) / sum(!is.na(x)), 
                                    n6 = sum(abs(x) > 6) ,
                                    p6 = 100 * sum(abs(x) > 6) / sum(!is.na(x))), 3))

aggregate(relse ~ wc + sa , 
          data = subset(dta1.stat, dfname=="cmp"), 
          FUN = function(x) round(c(n = sum(!is.na(x)),
                                    n10 = sum(abs(x) > 10) ,
                                    p10 = 100 * sum(abs(x) > 10) / sum(!is.na(x)), 
                                    n6 = sum(abs(x) > 6) ,
                                    p6 = 100 * sum(abs(x) > 6) / sum(!is.na(x))), 3))
```

#### KC:

```{r se_kc}

aggregate(relse ~ corrscenario + icc , 
          data = subset(dta1.stat, dfname=="cmp" & sa == "kc" & wc == "Exchangeable"), 
          FUN = function(x) round(c(n = sum(!is.na(x)),
                                    n10 = sum(abs(x) > 10) ,
                                    p10 = 100 * sum(abs(x) > 10) / sum(!is.na(x))), 3))

```

#### FG:

```{r se_fg}
setNames(aggregate(relse ~ wc +icc , 
                   data = subset(dta1.stat, dfname=="cmp" & sa == "fg"), 
                   FUN = function(x) round(summary(x), 3)), rep("",3))

```

#### MD:

```{r se_md}
setNames(aggregate(relse ~ icc , 
                   data = subset(dta1.stat, dfname=="cmp" & sa == "md"), 
                   FUN = function(x) round(summary(x), 3)), rep("",2))

setNames(aggregate(relse ~ Varying_cluster_size , 
                   data = subset(dta1.stat, dfname=="cmp" & sa == "md"), 
                   FUN = function(x) round(summary(x), 3)), rep("",2))

```

#### MBN:

```{r se_mbn}
setNames(aggregate(relse ~ sequences , 
                   data = subset(dta1.stat, dfname=="cmp" & sa == "mbn"), 
                   FUN = function(x) round(summary(x), 3)), rep("",2))

aggregate(relse ~ sequences , 
          data = subset(dta1.stat, dfname=="cmp" & sa == "mbn"), 
          FUN = function(x) round(c(n = sum(!is.na(x)),
                                    n10 = sum(abs(x) > 10) ,
                                    p10 = 100 * sum(abs(x) > 10) / sum(!is.na(x)), 
                                    n6 = sum(abs(x) > 6) ,
                                    p6 = 100 * sum(abs(x) > 6) / sum(!is.na(x))), 3))

aggregate(relse ~ Varying_cluster_size , 
          data = subset(dta1.stat, dfname=="cmp" & sa == "mbn"), 
          FUN = function(x) round(c(n = sum(!is.na(x)),
                                    n10 = sum(abs(x) > 10) ,
                                    p10 = 100 * sum(abs(x) > 10) / sum(!is.na(x)), 
                                    n6 = sum(abs(x) > 6) ,
                                    p6 = 100 * sum(abs(x) > 6) / sum(!is.na(x)),
                                    mean = mean(x)), 3))

```

#### MW:

```{r se_mw}
setNames(aggregate(relse ~ sequences , 
                   data = subset(dta1.stat, dfname=="cmp" & sa == "mw"), 
                   FUN = function(x) round(summary(x), 3)), rep("",2))

aggregate(relse ~ sequences , 
          data = subset(dta1.stat, dfname=="cmp" & sa == "mw"), 
          FUN = function(x) round(c(n = sum(!is.na(x)),
                                    n10 = sum(abs(x) > 10) ,
                                    p10 = 100 * sum(abs(x) > 10) / sum(!is.na(x)), 
                                    n6 = sum(abs(x) > 6) ,
                                    p6 = 100 * sum(abs(x) > 6) / sum(!is.na(x))), 3))


aggregate(relse ~ sequences + Varying_cluster_size , 
          data = subset(dta1.stat, dfname=="cmp" & sa == "mw"), 
          FUN = function(x) round(c(n = sum(!is.na(x)),
                                    n10 = sum(abs(x) > 10) ,
                                    p10 = 100 * sum(abs(x) > 10) / sum(!is.na(x)), 
                                    n6 = sum(abs(x) > 6) ,
                                    p6 = 100 * sum(abs(x) > 6) / sum(!is.na(x)),
                                    mean = mean(x)), 3))
```

### Degrees of freedom

```{r df}
setNames(aggregate(meandf ~ dfname + sa, 
                   data = subset(dta1.stat, sa %in% c("lz","fg","kc")), 
                   FUN = function(x) round(c(mean = mean(x), 
                                             sd = sd(x)), 3)), rep("",2))

setNames(aggregate(vardf ~ dfname + sa, 
                   data = subset(dta1.stat, sa %in% c("lz","fg","kc")), 
                   FUN = function(x) round(c(mean = mean(x), 
                                             sd = sd(x)), 3)), rep("",2))

setNames(aggregate(meandf ~ dfname + sa + sequences, 
                   data = subset(dta1.stat, sa %in% c("lz","fg","kc")), 
                   FUN = function(x) round(c(mean = mean(x), 
                                             sd = sd(x)), 3)), rep("",2))

setNames(aggregate(vardf ~ dfname + sa  + sequences, 
                   data = subset(dta1.stat, sa %in% c("lz","fg","kc")), 
                   FUN = function(x) round(c(mean = mean(x), 
                                             sd = sd(x)), 3)), rep("",2))

setNames(aggregate(meandf ~ dfname + sequences, 
                   data = subset(dta1.stat, sa == "fg" & Working_correlation == "Independent" ), 
                   FUN = function(x) round(c(mean = mean(x), 
                                             sd = sd(x)), 3)), rep("",2))

setNames(aggregate(vardf ~ dfname  + sequences, 
                   data = subset(dta1.stat, sa == "fg" & Working_correlation == "Independent"), 
                   FUN = function(x) round(c(mean = sqrt(mean(x)), 
                                             sd = sd(x)), 3)), rep("",2))

setNames(aggregate(vardf ~ dfname , 
                   data = subset(dta1.stat, sa == "fg" & Working_correlation == "Independent"), 
                   FUN = function(x) round(c(mean = sqrt(mean(x)), 
                                             sd = sd(x)), 3)), rep("",2))
```

### Coverage

```{r cov_histogram}


ggplot(data = subset(dta1.stat, sa %in% c("fg", "kc")), aes(x = coverage)) + 
  geom_vline(xintercept = 95, linetype = "longdash", color = "grey80", size = 0.5) +
  geom_vline(xintercept = 93.6, linetype = "longdash", color = "grey80", size = 0.5) +
  geom_vline(xintercept = 96.4, linetype = "longdash", color = "grey80", size = 0.5) +
  geom_histogram(bins = 20) + 
  facet_grid(DF ~ wc + SA) +
  xlab("95% confidence interval coverage") +
  scale_y_continuous(breaks = function(x) c(0,floor(x[2]))) +
  scale_x_continuous(labels = function(x) format(x,digits = 1,scientific = FALSE)) +
  theme

ggsave("./output/phase1_coverage.emf", width = 16, height = 12, units = "cm")
ggsave("./output/phase1_coverage.eps", width = 16, height = 12, units = "cm")


ggplot(data = subset(dta1.stat, sa %in% c("fg", "kc")), aes(x = coverage, fill = icc)) + 
  geom_vline(xintercept = 95, linetype = "longdash", color = "grey80", size = 0.5) +
  geom_vline(xintercept = 93.6, linetype = "longdash", color = "grey80", size = 0.5) +
  geom_vline(xintercept = 96.4, linetype = "longdash", color = "grey80", size = 0.5) +
  geom_histogram(bins = 20) + 
  facet_grid(DF ~ wc + SA) +
  xlab("95% confidence interval coverage") +
  scale_y_continuous(breaks = function(x) c(0,floor(x[2]))) +
  scale_x_continuous(labels = function(x) format(x,digits = 1,scientific = FALSE)) +
  theme

aggregate(coverage ~ wc + dfname + icc, 
          data = subset(dta1.stat, sa == "fg"), 
          FUN = function(x) mean = round(c(mean(x),
                                            p_over = 100 * sum(x > 96.4) / sum(!is.na(x)), 
                                           p_und = 100 * sum(x < 93.6) / sum(!is.na(x))),2))

```


## Phase 2

```{r scenarios2}
print("Number of scenarios:")

 length(unique(dta2.stat$scenario))
 
print("ICC:")

 kable(table(dta2.stat$ICC))

print("Correlation structure:")

 kable(table(dta2.stat$Correlation_structure))
 
print("Sequences:")

 kable(table(dta2.stat$Sequences))
 
print("Clusters:")

 kable(table(dta2.stat$clusters))

print("Cluster size:")

 kable(table(dta2.stat$Mean_cluster_size))

 kable(table(dta2.stat$Varying_cluster_size))

print("Which scenarios have cluster size 300?")
  kable(unique(dta2.stat[dta2.stat$Mean_cluster_size == "300", c("ICC", "Correlation_structure", "Sequences", "Clusters", "Varying_cluster_size")]))
```

### Convergence

```{r convergence2}
summary(dta2.stat$convergep)
```

### Bias
```{r bias_numbers2}
round(summary(dta2.stat$stdbias), 3)

round(summary(dta2.stat$pbias), 3)

ggplot(data = subset(dta2.stat, mdl %in% c("fg.cmp")), aes(x = stdbias)) + 
  facet_wrap( ~ wc) +
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey80", size = 1)+
  geom_vline(xintercept = -10, linetype = "longdash", color = "grey80", size = 1)+
  geom_vline(xintercept = 10, linetype = "longdash", color = "grey80", size = 1) +
  geom_histogram(bins = 20) + 
  xlab("Intervention effect estimate standardised bias") +
  scale_y_continuous(breaks = function(x) c(0,floor(x[2]))) +
  theme

ggsave("./output/phase2_rxbias.pdf", width = 16, height = 12, units = "cm")
```

### Standard errors

```{r se_histogram2}


ggplot(data = subset(dta2.stat, mdl == "lz.inf" ), aes(x = relsetrunc)) + 
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey80", size = 0.5) +
  geom_vline(xintercept = -10, linetype = "longdash", color = "grey80", size = 0.5) +
  geom_vline(xintercept = 10, linetype = "longdash", color = "grey80", size = 0.5) +
  geom_histogram(bins = 30) + 
  facet_grid(clusters ~  wc ) +
  labs(y = NULL, x = "Standard error relative error (%)") +
  scale_x_continuous(breaks = c(-20, 0, 20, 30), labels = c("-20", "0", "20", ">30")) +
  scale_y_continuous(breaks = function(x) c(0,floor(x[2]))) +
  theme

ggsave("./output/phase2_se_hist_uncorr.pdf", width = 16, height = 12, units = "cm")


ggplot(data = subset(dta2.stat, mdl %in% c("kc.cmp", "fg.cmp") & clusters %in% c(6,12,18,24,54)), aes(x = relsetrunc)) + 
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey80", size = 0.5) +
  geom_vline(xintercept = -10, linetype = "longdash", color = "grey80", size = 0.5) +
  geom_vline(xintercept = 10, linetype = "longdash", color = "grey80", size = 0.5) +
  geom_histogram(bins = 30) + 
  facet_grid(SA + clusters ~  wc ) +
  labs(y = NULL, x = "Standard error relative error (%)") +
  scale_x_continuous(breaks = c(-20, 0, 20, 30), labels = c("-20", "0", "20", ">30")) +
  scale_y_continuous(breaks = function(x) c(0,floor(x[2]))) +
  theme

ggsave("./output/phase2_se_hist.emf", width = 16, height = 12, units = "cm")
ggsave("./output/phase2_se_hist.eps", width = 16, height = 12, units = "cm")

ggplot(data = subset(dta2.stat, mdl %in% c("kc.cmp", "fg.cmp") & clusters %in% c(6,12,18,24,54)), aes(x = relsetrunc, fill = ICC)) + 
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey80", size = 0.5) +
  geom_vline(xintercept = -10, linetype = "longdash", color = "grey80", size = 0.5) +
  geom_vline(xintercept = 10, linetype = "longdash", color = "grey80", size = 0.5) +
  geom_histogram(bins = 30) + 
  facet_grid(SA + clusters ~  wc ) +
  labs(y = NULL, x = "Standard error relative error (%)") +
  scale_x_continuous(breaks = c(-20, 0, 20, 30), labels = c("-20", "0", "20", ">30")) +
  scale_y_continuous(breaks = function(x) c(0,floor(x[2]))) +
  theme

ggsave("./output/phase2_se_hist_ICC.pdf", width = 16, height = 12, units = "cm")


ggplot(data = subset(dta2.stat, mdl %in% c("kc.cmp", "fg.cmp")  & clusters %in% c(6,12,18,24,54)), aes(x = relsetrunc, fill = Varying_cluster_size)) + 
  geom_vline(xintercept = 0, linetype = "longdash", color = "grey80", size = 0.5) +
  geom_vline(xintercept = -10, linetype = "longdash", color = "grey80", size = 0.5) +
  geom_vline(xintercept = 10, linetype = "longdash", color = "grey80", size = 0.5) +
  geom_histogram(bins = 30) + 
  facet_grid(SA + clusters ~  wc ) +
  labs(y = NULL, x = "Standard error relative error (%)") +
  scale_x_continuous(breaks = c(-20, 0, 20, 30), labels = c("-20", "0", "20", ">30")) +
  scale_y_continuous(breaks = function(x) c(0,floor(x[2]))) +
  theme

ggsave("./output/phase2_se_hist_varying_cluster_size.pdf", width = 16, height = 12, units = "cm")



```


```{r se_n2}
setNames(aggregate(relse ~ sa , 
                   data = subset(dta2.stat, dfname=="cmp"), 
                   FUN = function(x) round(summary(x), 3)), rep("",2))


aggregate(relse ~ sa , 
          data = subset(dta2.stat, dfname=="cmp"), 
          FUN = function(x) round(c(n = sum(!is.na(x)),
                                    n10 = sum(abs(x) > 10) ,
                                    p10 = 100 * sum(abs(x) > 10) / sum(!is.na(x)), 
                                    n8 = sum(abs(x) > 8) ,
                                    p8 = 100 * sum(abs(x) > 8) / sum(!is.na(x)), 
                                    n6 = sum(abs(x) > 6) ,
                                    p6 = 100 * sum(abs(x) > 6) / sum(!is.na(x))), 3))

```

#### Uncorrected:

```{r se_uncorr2}

setNames(aggregate(relse ~ Clusters , 
                   data = subset(dta2.stat, dfname=="cmp" & sa == "lz"), 
                   FUN = function(x) round(summary(x), 3)), rep("",2))

```


#### KC:

```{r se_kc2}

setNames(aggregate(relse ~ Clusters + wc , 
                   data = subset(dta2.stat, dfname=="cmp" & sa == "kc"), 
                   FUN = function(x) round(summary(x), 3)), rep("",2))

setNames(aggregate(relse ~ Mean_cluster_size, 
                   data = subset(dta2.stat, dfname=="cmp" & sa == "kc" & wc == "Exchangeable" & Correlation_structure == "Exchangeable"), 
                   FUN = function(x) round(summary(x), 3)), rep("",2))

```

#### FG:

```{r se_fg2}

aggregate(relse ~ clusters , 
          data = subset(dta2.stat,  
                        mdl == "fg.cmp" & wc == "Independent" ),
          FUN = function(x) round(c(mean = mean(x), 
                                    sd = sd(x),
                                    n = sum(!is.na(x)),
                                    n10 = sum(abs(x) > 10) ,
                                    p10 = 100 * sum(abs(x) > 10) / sum(!is.na(x))), 3))
aggregate(relse ~ clusters +wc, 
          data = subset(dta2.stat,  
                        mdl == "fg.cmp"),
          FUN = function(x) round(c(mean = mean(x), 
                                    sd = sd(x),
                                    p10 = 100 * sum(abs(x) > 10) / sum(!is.na(x))), 3))

aggregate(relse ~ clusters  + icc , 
          data = subset(dta2.stat,  
                        mdl == "fg.cmp" & wc == "Exchangeable" ),
          FUN = function(x) round(c(mean = mean(x), 
                                    sd = sd(x),
                                    n = sum(!is.na(x)),
                                    n10 = sum(abs(x) > 10) ,
                                    p10 = 100 * sum(abs(x) > 10) / sum(!is.na(x))), 3))

aggregate(relse ~ icc + Varying_cluster_size , 
          data = subset(dta2.stat,  
                        mdl == "fg.cmp" & wc == "Exchangeable"& Clusters %in% c(6,12)),
          FUN = function(x) round(c(mean = mean(x), 
                                    sd = sd(x),
                                    n = sum(!is.na(x)),
                                    n10 = sum(abs(x) > 10) ,
                                    p10 = 100 * sum(abs(x) > 10) / sum(!is.na(x))), 3))

```

### Degrees of freedom

```{r df2_1, echo = FALSE}


dta2.stat.wide <- reshape(direction = "wide",
                          data = dta2.stat[dta2.stat$mdl %in% c("fg.cmp", "fg.fgd5"), 
                                           c("scenario", "clusters", "icc", "corrscenario", "sequences", "Mean_cluster_size", "cv cluster size", "wc", "meandf", "DF")],
                          idvar =  c("scenario", "clusters", "icc", "corrscenario", "sequences", "Mean_cluster_size", "cv cluster size", "wc"),
                          v.names = "meandf",
                          timevar = "DF")

dta2.stat.wide$diff <- (dta2.stat.wide$meandf.FG - dta2.stat.wide$'meandf.C-P') 

```

```{r df2_2}

aggregate(cbind(meandf.FG, `meandf.C-P`, diff) ~ clusters , 
          data = subset(dta2.stat.wide, Mean_cluster_size != "300"), 
          FUN = function(x) round(c(mean = mean(x), 
                                    sd = sd(x)), 3))

ggplot(data = subset(dta2.stat, dfname == "cmp"), 
       aes(x = meandf, y = dfdiff[,1], color = `cv cluster size`, shape = sequences)) + 
  geom_hline(yintercept = 0, linetype = "longdash", color = "grey80", size = 0.5) +
  geom_point(size = 0.8, stroke = 1.2) +
  scale_color_grey() +
  scale_shape_manual( values = c(4, 1)) +
  xlab("Clusters - parameters") +
  ylab(expression(DF[FG] -DF[C-P])) +
  theme

ggsave("./output/phase2_df.pdf", width = 16, height = 12, units = "cm")
```


### Coverage

```{r cov_histogram2}

ggplot(data = subset(dta2.stat, sa %in% c("fg", "kc") & clusters %in% c(6,12,18,24,54)), aes(x = coverage)) + 
  geom_histogram(bins = 25) + 
  facet_grid(DF  + clusters ~ wc + SA) +
  geom_vline(xintercept = 95, linetype = "longdash", color = "grey80", size = 0.5) + 
  geom_vline(xintercept = 93.6, linetype = "longdash", color = "grey80", size = 0.5) + 
  geom_vline(xintercept = 96.4, linetype = "longdash", color = "grey80", size = 0.5) +
  xlab("95% confidence interval coverage") +
  scale_y_continuous(breaks = function(x) c(0,floor(x[2]))) +
  theme

ggsave("./output/phase2_coverage_corr.emf", width = 16, height = 12, units = "cm")
ggsave("./output/phase2_coverage_corr.eps", width = 16, height = 12, units = "cm")

ggplot(data = subset(dta2.stat, sa %in% c("fg", "kc") & clusters %in% c(6,12,18,24,54)), aes(x = coverage, fill = sequences)) + 
  geom_histogram(bins = 25) + 
  facet_grid(DF + clusters ~ wc + SA) +
  geom_vline(xintercept = 95, linetype = "longdash", color = "grey80", size = 0.5) + 
  geom_vline(xintercept = 93.6, linetype = "longdash", color = "grey80", size = 0.5) + 
  geom_vline(xintercept = 96.4, linetype = "longdash", color = "grey80", size = 0.5) +
  xlab("95% confidence interval coverage") +
  scale_y_continuous(breaks = function(x) c(0,floor(x[2]))) +
  theme

ggsave("./output/phase2_coverage_corr_seq.pdf", width = 16, height = 12, units = "cm")

ggplot(data = subset(dta2.stat, sa %in% c("fg", "kc") & clusters %in% c(6,12,24,48)), aes(x = coverage, fill = icc)) + 
  geom_histogram(bins = 25) + 
  facet_grid(DF + clusters ~ wc + SA) +
  geom_vline(xintercept = 95, linetype = "longdash", color = "grey80", size = 0.5) + 
  geom_vline(xintercept = 93.6, linetype = "longdash", color = "grey80", size = 0.5) + 
  geom_vline(xintercept = 96.4, linetype = "longdash", color = "grey80", size = 0.5) +
  xlab("95% confidence interval coverage") +
  scale_y_continuous(breaks = function(x) c(0,floor(x[2]))) +
  theme

ggsave("./output/phase2_coverage_corr_icc.pdf", width = 16, height = 12, units = "cm")

ggplot(data = subset(dta2.stat, (sa %in% c("lz") | mdl == "lz.inf") & clusters > 18), aes(x = coverage)) + 
  geom_histogram(bins = 15) + 
  facet_grid(clusters ~  wc+ DF) +
  geom_vline(xintercept = 95, linetype = "longdash", color = "grey80", size = 0.5) + 
  geom_vline(xintercept = 93.6, linetype = "longdash", color = "grey80", size = 0.5) + 
  geom_vline(xintercept = 96.4, linetype = "longdash", color = "grey80", size = 0.5) +
  xlab("95% confidence interval coverage") +
  scale_y_continuous(breaks = function(x) c(0,floor(x[2]))) +
  theme

ggsave("./output/phase2_coverage_uncorr.pdf", width = 16, height = 12, units = "cm")

```

#### Uncorrected

```{r cov_n2}
aggregate(coverage ~ clusters + dfname, 
          data = subset(dta2.stat, sa == "lz"), 
          FUN = function(x) round(c(n = sum(!is.na(x)), 
                                    overc = sum(x > 96.4),
                                    p_overc = 100 * sum(x > 96.4) / sum(!is.na(x)), 
                                    underc = sum(x < 93.6), 
                                    p_underc = 100 * sum(x < 93.6) / sum(!is.na(x))),2))
```

#### KC

```{r cov_n2_kc}
aggregate(coverage ~ clusters + wc + dfname, 
          data = subset(dta2.stat, sa == "fg"), 
          FUN = function(x) mean = round(c(mean(x),
                                            p_over = 100 * sum(x > 96.4) / sum(!is.na(x)), 
                                           p_und = 100 * sum(x < 93.6) / sum(!is.na(x))),2))
aggregate(coverage ~ wc + dfname, 
          data = subset(dta2.stat, sa == "kc"), 
          FUN = function(x) round(c(n = sum(!is.na(x)), 
                                    overc = sum(x > 96.4),
                                    p_overc = 100 * sum(x > 96.4) / sum(!is.na(x)), 
                                    underc = sum(x < 93.6), 
                                    p_underc = 100 * sum(x < 93.6) / sum(!is.na(x))),2))
```


#### FG

```{r cov_n2_fg}



aggregate(coverage ~ wc + dfname, 
          data = subset(dta2.stat, sa == "fg"), 
          FUN = function(x) round(c(mean = mean(x), 
                                    n = sum(!is.na(x)), 
                                    over = sum(x > 96.4),
                                    p_over = 100 * sum(x > 96.4) / sum(!is.na(x)), 
                                    und = sum(x < 93.6), 
                                    p_und = 100 * sum(x < 93.6) / sum(!is.na(x))),2))

aggregate(coverage ~ clusters + wc + dfname, 
          data = subset(dta2.stat, sa == "fg"), 
          FUN = function(x) mean = round(c(mean(x),
                                            p_over = 100 * sum(x > 96.4) / sum(!is.na(x)), 
                                           p_und = 100 * sum(x < 93.6) / sum(!is.na(x))),2))

aggregate(coverage ~ clusters + wc + icc, 
          data = subset(dta2.stat, sa == "fg"), 
          FUN = function(x) mean = round(mean(x),2))

```

#### Degrees of freedom

```{r cov_n2_df}

aggregate(coverage ~ dfname, 
          data = dta2.stat, 
          FUN = function(x) round(c(n = sum(!is.na(x)), 
                                    overc = sum(x > 96.4),
                                    p_overc = 100 * sum(x > 96.4) / sum(!is.na(x)), 
                                    underc = sum(x < 93.6), 
                                    p_underc = 100 * sum(x < 93.6) / sum(!is.na(x))),2))


```

### Power

#### Power: sa diff with indep wc

```{r powersa}

dta2.stat.wide <- reshape(direction = "wide",
                          data = dta2.stat[dta2.stat$mdl %in% c("kc.fgd5", "fg.fgd5", "kc.cmp", "fg.cmp") & dta2.stat$clusters > 6, 
                                           c("scenario", "clusters", "icc", "corrscenario", "sequences", "Mean_cluster_size", "cv cluster size", "wc", "power", "DF", "sa")],
                          idvar =  c("scenario", "clusters", "icc", "corrscenario", "sequences", "Mean_cluster_size", "cv cluster size", "DF", "wc"),
                          v.names = "power",
                          timevar = "sa")

dta2.stat.wide$av <- (dta2.stat.wide$power.fg + dta2.stat.wide$power.kc) / 2
dta2.stat.wide$diff <- dta2.stat.wide$power.fg - dta2.stat.wide$power.kc
dta2.stat.wide$reldiff <- (dta2.stat.wide$power.fg + 1) / (dta2.stat.wide$power.kc + 1)
dta2.stat.wide$logreldiff <- log(dta2.stat.wide$reldiff)

ggplot(data = subset(dta2.stat.wide, wc == "Independent"), aes(x = diff)) + 
  geom_histogram() +
  xlab("Difference in power (FG - KC)") +
  theme

ggsave("./output/phase2_power_sa.pdf", width = 16, height = 12, units = "cm")

sumdiff <- aggregate(diff ~ DF, data = subset(dta2.stat.wide, wc == "Independent"), FUN = function(x) c(mean(x), sd(x)))
sumdiff$mean <- sumdiff$diff[,1]
sumdiff$sd <- sumdiff$diff[,2]
sumdiff$upper <- sumdiff$mean + 1.96 * sumdiff$sd
sumdiff$lower <- sumdiff$mean - 1.96 * sumdiff$sd

ggplot(data = subset(dta2.stat.wide, wc == "Independent"), aes(x = av, y = diff)) + 
  facet_grid(DF ~.) +
  geom_hline(yintercept = 0) +
  geom_hline(data = sumdiff, aes(yintercept = mean), linetype = "longdash", color = "grey80") +
  geom_hline(data = sumdiff, aes(yintercept = upper), linetype = "longdash", color = "grey80") +
  geom_hline(data = sumdiff, aes(yintercept = lower), linetype = "longdash", color = "grey80") +
  geom_point() +
  theme


aggregate(diff ~ wc, 
          data = dta2.stat.wide,
          FUN = function(x) round(c(n =  sum(!is.na(x)),
                                    mean = (mean(x)), 
                                    median = (median(x)), 
                                    p25 = (quantile(x,0.25)),
                                    p25 = (quantile(x,0.75))), 2))

dta2.stat.wide$clusters <- factor(dta2.stat.wide$clusters)
dta2.stat.wide$cv <- dta2.stat.wide$`cv cluster size`

mdl <- lm(diff ~ clusters + sequences + corrscenario + icc + Mean_cluster_size + cv,
   data = subset(dta2.stat.wide, wc == "Independent"))

coef(summary(mdl))
anova(mdl)
ggeffect(mdl, given.values = "equal")


```


#### Power: df diff with indep wc 

```{r powerdf}

dta2.stat.wide <- reshape(direction = "wide",
                          data = dta2.stat[dta2.stat$mdl %in% c("kc.fgd5", "fg.fgd5", "kc.cmp", "fg.cmp") & dta2.stat$wc == "Independent", 
                                           c("scenario", "clusters", "icc", "corrscenario", "sequences", "Mean_cluster_size", "cv cluster size", "wc", "power", "DF", "SA")],
                          idvar =  c("scenario", "clusters", "icc", "corrscenario", "sequences", "Mean_cluster_size", "cv cluster size", "wc", "SA"),
                          v.names = "power",
                          timevar = "DF")

dta2.stat.wide$diff <- dta2.stat.wide$power.FG - dta2.stat.wide$`power.C-P`

dta2.stat.wide$av <- (dta2.stat.wide$power.FG + dta2.stat.wide$`power.C-P`) / 2
dta2.stat.wide$reldiff <- (dta2.stat.wide$power.FG + 1) / (dta2.stat.wide$`power.C-P` + 1)
dta2.stat.wide$logreldiff <- log(dta2.stat.wide$reldiff)

ggplot(data = dta2.stat.wide, aes(x = diff)) + 
  facet_grid(clusters~.) +
  geom_histogram() +
  xlab(expression(paste("Difference in power (", DF[FG] - DF[C-P] ,")"))) +
  theme

ggsave("./output/phase2_power_DF.pdf", width = 16, height = 12, units = "cm")

sumdiff <- aggregate(diff ~ SA, data = dta2.stat.wide, FUN = function(x) c(mean(x), sd(x)))
sumdiff$mean <- sumdiff$diff[,1]
sumdiff$sd <- sumdiff$diff[,2]
sumdiff$upper <- sumdiff$mean + 1.96 * sumdiff$sd
sumdiff$lower <- sumdiff$mean - 1.96 * sumdiff$sd

ggplot(data = dta2.stat.wide, aes(x = av, y = diff )) + 
  facet_grid(SA ~.) +
  geom_hline(yintercept = 1) +
  geom_hline(data = sumdiff, aes(yintercept = mean), linetype = "longdash", color = "grey80") +
  geom_hline(data = sumdiff, aes(yintercept = upper), linetype = "longdash", color = "grey80") +
  geom_hline(data = sumdiff, aes(yintercept = lower), linetype = "longdash", color = "grey80") +
  geom_point() +
  theme


aggregate(diff ~ clusters, 
          data = dta2.stat.wide,
          FUN = function(x) round(c(n =  sum(!is.na(x)),
                                    mean = (mean(x)), 
                                    median = (median(x)), 
                                    p25 = (quantile(x,0.25)),
                                    p25 = (quantile(x,0.75))),2))

dta2.stat.wide$clusters <- factor(dta2.stat.wide$clusters)
dta2.stat.wide$cv <- dta2.stat.wide$`cv cluster size`


mdl <- lm(diff ~ clusters + sequences + corrscenario + icc + Mean_cluster_size + cv,
   data = dta2.stat.wide)

coef(summary(mdl))
anova(mdl)
ggeffect(mdl, given.values = "equal")
# meff <- ggeffect(mdl, given.values = "equal")
# meff <- do.call(rbind, meff)
# cbind(meff[,c(1,6)], round(exp(meff[,c(2,4,5)]),3))


```

#### Power: wc diff with kc sa and FG DF

``` {r powerwc}


# Reshape by wc

dta2.stat.wide <- reshape(direction = "wide",
                          data = dta2.stat[dta2.stat$mdl %in% c("kc.fgd5", "fg.fgd5"), 
                                           c("scenario", "clusters", "icc", "corrscenario", "sequences", "Mean_cluster_size", "cv cluster size", "wc", "power", "DF", "SA")],
                          idvar =  c("scenario", "clusters", "icc", "corrscenario", "sequences", "Mean_cluster_size", "cv cluster size", "DF", "SA"),
                          v.names = "power",
                          timevar = "wc")

# Calculate differences

dta2.stat.wide$av <- ((dta2.stat.wide$power.Exchangeable ) + ( dta2.stat.wide$power.Independent )) /2 
dta2.stat.wide$diff <- ((dta2.stat.wide$power.Exchangeable ) - ( dta2.stat.wide$power.Independent )) 
dta2.stat.wide$reldiff <- ((dta2.stat.wide$power.Exchangeable + 1) / ( dta2.stat.wide$power.Independent + 1)) 
dta2.stat.wide$logreldiff <- log(dta2.stat.wide$reldiff)

# Plot EWM - IWM against average

sumdiff <- aggregate(diff ~ SA, data = dta2.stat.wide, FUN = function(x) c(mean(x), sd(x)))
sumdiff$mean <- sumdiff$diff[,1]
sumdiff$sd <- sumdiff$diff[,2]
sumdiff$upper <- sumdiff$mean + 1.96 * sumdiff$sd
sumdiff$lower <- sumdiff$mean - 1.96 * sumdiff$sd

ggplot(data = dta2.stat.wide, aes(x = av, y = diff, color = Mean_cluster_size)) + 
  facet_grid(SA ~.) +
  geom_hline(yintercept = 0) +
  geom_hline(data = sumdiff, aes(yintercept = mean), linetype = "longdash", color = "grey80") +
  geom_hline(data = sumdiff, aes(yintercept = upper), linetype = "longdash", color = "grey80") +
  geom_hline(data = sumdiff, aes(yintercept = lower), linetype = "longdash", color = "grey80") +
  geom_point() +
  theme

# Plot EWM / IWM against average

sumreldiff <- aggregate(logreldiff ~ SA, data = dta2.stat.wide, FUN = function(x) c(mean(x), sd(x)))
sumreldiff$mean <- sumreldiff$logreldiff[,1]
sumreldiff$sd <- sumreldiff$logreldiff[,2]
sumreldiff$emean <- exp(sumreldiff$mean)
sumreldiff$upper <- exp(sumreldiff$mean + 1.96 * sumreldiff$sd)
sumreldiff$lower <- exp(sumreldiff$mean - 1.96 * sumreldiff$sd)

ggplot(data = dta2.stat.wide, aes(x = av, y = reldiff, color = Mean_cluster_size)) + 
  facet_grid(SA ~.) +
  geom_hline(yintercept = 1) +
  geom_hline(data = sumreldiff, aes(yintercept = emean), linetype = "longdash", color = "grey80") +
  geom_hline(data = sumreldiff, aes(yintercept = upper), linetype = "longdash", color = "grey80") +
  geom_hline(data = sumreldiff, aes(yintercept = lower), linetype = "longdash", color = "grey80") +
  geom_point() +
  scale_y_continuous(trans='log2') +
  theme

ggplot(data = dta2.stat.wide, aes(x = diff)) + 
  facet_grid(SA ~ .) +
  geom_vline(xintercept = 1) +
  geom_histogram(bins=40) +
  xlab("Difference in power (Exchangeable - Independent)") +
  theme

ggsave("./output/phase2_power_wc.pdf", width = 16, height = 12, units = "cm")


aggregate(diff ~ SA, 
          data = subset(dta2.stat.wide, DF == "FG"),
          FUN = function(x) round(c(n =  sum(!is.na(x)),
                                    mean = (mean(x)), 
                                    median = (median(x)), 
                                    p25 = (quantile(x,0.25)),
                                    p25 = (quantile(x,0.75))),2))

dta2.stat.wide$clusters <- factor(dta2.stat.wide$clusters)
dta2.stat.wide$cv <- dta2.stat.wide$`cv cluster size`

mdl <- lm(diff ~ clusters + sequences + corrscenario + icc + Mean_cluster_size + cv,
   data = subset(dta2.stat.wide, SA == "KC"), na.action = na.exclude )

coef(summary(mdl))
anova(mdl)

ggeffect(mdl, given.values = "equal")

# meff <- do.call(rbind, ggeffect(mdl, given.values = "equal"))
# cbind(meff[,c(1,6)], round(exp(meff[,c(2,4,5)]),3))

mdl <- lm(diff ~ clusters+ sequences + corrscenario + icc + Mean_cluster_size + cv,
   data = subset(dta2.stat.wide, SA == "FG"))

#coef(summary(mdl))
anova(mdl)

ggeffect(mdl, given.values = "equal")


# meff <- do.call(rbind, ggeffect(mdl, given.values = "equal"))
# cbind(meff[,c(1,6)], round(exp(meff[,c(2,4,5)]),3))

# Can also look at marginal effect fixing cluster size:
#meff <- ggeffect(mdl, given.values = c(clusters12 = 1/7, clusters18 = 1/7, clusters24 = 1/7, clusters42 = 1/7, clusters48 = 1/7, clusters54 = 1/7, sequences6 = 1/2, "corrscenarioAR r=0.6" = 1/4, "corrscenarioAR r=0.8"  = 1/4, "corrscenarioReduced intervention" =1/4, icc0.05 = 1/3, icc0.1 = 1/3, Mean_cluster_size60 = 0, Mean_cluster_size300 = 1, cv0.4 =1/2))


temp <- dta2.stat[dta2.stat$wc == "Exchangeable" & dta2.stat$mdl == "fg.fgd5",]

temp <- merge(temp, dta2.stat.wide, by = c("scenario", "clusters", "icc", "corrscenario", "sequences", "Mean_cluster_size", "cv cluster size", "DF", "SA"))

ggplot(data = subset(temp, Mean_cluster_size == "300"), aes(x = coverage, y = diff, color=factor(clusters))) + 
  facet_grid(icc ~ corrscenario) + 
  geom_vline(xintercept = 95) + 
  geom_point()

```


#### Difference in SEs by correlation structure

``` {r sewc}

# Reshape by WC
dta2.stat.wide <- reshape(direction = "wide",
                          data = dta2.stat[dta2.stat$mdl %in% c("kc.fgd5", "fg.fgd5")& dta2.stat$clusters > 12, 
                                           c("scenario", "clusters", "icc", "corrscenario", "sequences", "Mean_cluster_size", "cv cluster size", "wc", "mbse", "DF", "SA")],
                          idvar =  c("scenario", "clusters", "icc", "corrscenario", "sequences", "Mean_cluster_size", "cv cluster size", "DF", "SA"),
                          v.names = "mbse",
                          timevar = "wc")

dta2.stat.wide$relseive <- dta2.stat.wide$mbse.Exchangeable / dta2.stat.wide$mbse.Independent

ggplot(data = dta2.stat.wide, aes(x = relseive)) + 
  facet_grid(SA ~ .) +
  geom_vline(xintercept = 1) +
  geom_histogram(bins=40) +
  xlab("Ratio of standard errors (Exchangeable / Independent)") +
  theme
```

